%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{textcomp}

% adjust the page margins
\usepackage[scale=0.82]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Sri}
\familyname{Raghavan}
\address{Carnegie Mellon University, SMC 4670}{Pittsburgh, PA 15289}    % optional, remove the line if not wanted
\mobile{832.735.7242}                    % optional, remove the line if not wanted
\email{srikrish@andrew.cmu.edu}                      % optional, remove the line if not wanted
\extrainfo{Twitter: @srir} % optional, remove the line if not wanted
\homepage{http://github.com/srir}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{Education}
\cventry{2010--2014}{Bachelors in Computer Science}{Carnegie Mellon 
  University}{Pittsburgh, PA}{}{GPA: 3.53}  % arguments 3 to 6 can be left 
\cventry{2006--2010}{High School}{Academy of Science and Technology}{The 
  Woodlands, TX}{}{Class Rank: 2/593, GPA: 5.251} \\
\section{Experience}
\cventry{2013--}{Software Engineering Intern}{Gumroad, Inc.}{San Francisco,
  CA}{}{A startup building http://gumroad.com, an awesome way for content 
  creators to share and sell their digital products.}
\cventry{2012--2013}{Software Engineering Intern}{Twitter, Inc.}{San Francisco,
  CA}{}{Worked on the Platform Services team, building parts of the internal
  Thrift-based remote procedure call API. Worked part-time for Twitter during
  the 2012-2013 school year.}
\cventry{2011--2013}{15-150 Teaching Assistant}{Carnegie Mellon 
University}{Pittsburgh, PA}{}{Principles of Functional Programming, a class 
that teaches functional programming in Standard ML with a focus on mathematical 
proofs of code.}
\cventry{2011--2011}{Web Development Intern}{Offline Labs, Inc.}{San Francisco, 
CA}{}{A seed-stage startup building S\=osh, an activity recommendation engine. 
Worked extensively with Python and Django. See http://sosh.com.}%
% Detailed achievements:%
% \begin{itemize}%
% \item Implemented a powerful AJAX-based search feature for activities in San Francisco
% \item Integration with Twilio API to provide mobile access to S\=osh
% \item Designed and implemented a modular, automatic content aggregator and 
%   feed/API scraper.
% \end{itemize}}
\\
\section{Skills}
\cvline{Programming Languages}{\small Python, JavaScript, Scala, Standard ML, C}
\cvline{Style}{\small Strong work ethic, team player, always looking to learn 
  more.} \\
\section{Projects}
\cventry{2013--}{Hamilton}{}{}{}{Web application, originally written for 
PennApps Spring 2013, to provide a simple interface for constructing and 
sharing vertex-edge graphs.}
\cventry{2012--}{tau}{}{}{}{Web application, originally written for Greylock 
Hackfest 2012, to provide a lightweight, simplified code review platform for 
instructors and students.}
\cventry{2010--2011}{ScheduleMatch}{}{}{}{Web application that works with the 
ScheduleMan class schedule planner at CMU to show users which of their Facebook 
friends share classes with them. Built using Python and Django.}
\end{document}
